---
title: '2016 Alumni surveys: Scheme Type Breakdown'
author: "CSC E&M Team"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  html_document: default
---


```{r setup, include = FALSE}

source("S:/SCHOLARSHIPS/CSC/SCHEMES/CSFP-IN/CSC-Evaluation/Data Management Crystal Snap IT/r_codebank/2016_sch_long/2016_sch_long_basicanalysis.r")

library(pacman)
pacman:: p_load(tidyverse, pander,knitr, RODBC)

set.alignment("left", permanent = T)
panderOptions("table.split.table",Inf)

```

This document relates to `r SurveyName` and is a intended as a short overview of basic findings by a key variable. Figures in tables are proportions (%) of the total (e.g. 89% of Split site Scholars replied 'Often') unless otherwise stated. For more detailed interpretation or explanation of the figures, please contact the evaluation team: [evaluation@cscuk.org.uk](mailto:evaluation@cscuk.org.uk)

# 1. Data overview

Counts of cases are not typically shown in the results tables; note should taken where the table below indicates few respondents in a particular category.

```{r, echo=FALSE}
overview_schtype %>% 
  select(-Variable,"Scheme Type"=Response,Cases=freq, 'Proportion (%)'=prop) %>% 
  pander
```

# 2. Current residency

```{r, echo=FALSE}
bind_rows(rescountry_schtype,resregion_schtype) %>% 
  filter(Response=="Home") %>% 
  select(-freq, -Response, "Scheme Type"=SchemeType) %>% 
  mutate(Variable = fct_recode(Variable, "Country"="resStatusCountry","Region"="resStatusRegion")) %>% 
  spread(Variable, prop) %>% 
  pander
```

# 3. Employment

Employment status:

```{r, echo=FALSE}
empcurrent_schtype %>% 
  select(-freq,-Variable, "Scheme Type"=SchemeType) %>% 
  mutate(Response = fct_recode(Response, "Other" = "Neither employed nor studying")) %>% 
  spread(Response, prop) %>% 
  select(contains("Scheme Type"), Employed, contains("Employed and studying"),Studying, Other) %>% 
  pander
```

Current sector of employment of Scholars (Note: percentages may not sum to 100%: proportions are of all Scholars in each category, including any not currently employed):

```{r, echo=FALSE}
empsector_schtype %>% 
  select(-freq,-Variable, "Scheme Type"=SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response, prop) %>% 
  pander
```

# 4. Further qualificiations

Study of additional qualifications post-Commonwealth Scholarship. Note: be cautious of low size for groups distorting figures for these questions.

Respondents who had undertaken additional qualifications since completing their Commonwealth Scholarship:

```{r, echo=FALSE}
acapostaward_schtype %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select( -Response,-Variable, "Proportion (%)"=prop,"Cases"=freq,"Scheme Type"=SchemeType) %>% 
  pander
```

Level of qualification studied (each level is shown as a proportion of respondents who had undertaken additional qualifications):

```{r, echo=FALSE}
acaquallevel_schtype %>% 
  select(-freq, -Variable, "Scheme Type"=SchemeType, "Degree studied"=Response) %>% 
  spread("Degree studied",prop) %>% 
  pander
```

# 5. Leadership activities

Workplace related leadership activities:

```{r, echo=FALSE}
bind_rows(ldrbudget_schtype, ldrmanaging_schtype, ldrsupervise_schtype,ldrstrategy_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq, -Response, "Scheme Type"=SchemeType) %>% 
  mutate(Variable = fct_recode(Variable,"Overseeing budgets"="LdrBudget","Managing Company / department" = "LdrManaging",
                               "Setting strategy"="LdrStrategy","Supervising others"="LdrSupervising")) %>% 
  spread(Variable, prop) %>% 
  pander
```

# 6. Skill application

Use of skills from Scholarship in various circumstances. Divided into three overall groups: Use of skills, knowledge transfer, and advocating for change.

__[6.1] Use of skills__

Three variables constitute the 'use of skills' group: application of skills learned during your studies in the workplace; application of skills learned during your studies outside of the workplace; and approaching a problem differently based on something learned during your studies.

Use of skills in the workplace:

```{r, echo=FALSE}
appskillwork_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

Use of skills outside of the workplace:

```{r, echo=FALSE}
appskillnonwork_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

Approach a problem differently:

```{r, echo=FALSE}
appapproach_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

__[6.2] Knowledge transfer__

Two variables constitute the 'knowledge transfer' group: teaching a colleague something learned during your studies and developing training resources for others based something learned during your studies.

Teaching a colleague:

```{r, echo=FALSE}
apptrain_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

Developing training resources:

```{r, echo=FALSE}
appresources_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

__[6.3] Advocacy and influencing change__

Two variables constitute the 'advocacy and influencing change' group: Encouraging senior managers to make change based on something learned during your studies and making a change to your organisation's working practice based on something learned during your studies.

Encouraging senior managers to make change:

```{r, echo=FALSE}
appadvocate_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

Personally making a change to organisational practice:

```{r, echo=FALSE}
appchange_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>%
  pander
```

# 7. Research activity

Overall involvement in academic research:

```{r, echo=FALSE}
resmain_schtype %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-Response,-Variable, "Scheme Type"=SchemeType,Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

__[7.1] Academic Productivity__

Results do not sum to 100% in each row because some Scholars are not involved in academic research activity at all: these respondents are excluded from the table, but the proportions shown are based on all Scholars within each category, not _only_ Scholars involved in academic research. The category "Never" thus means a Scholar who has indicated involvement in academic research generally, but has indicated that they are never involved in this specific academic activity (e.g. publishing journal articles). This applies to "7.1. Academic Productivity" and "7.3. Research Collaboration".

Publishing journal articles:

```{r, echo=FALSE}
rescomparticles_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>%
  pander
```

Involvement in academic projects:

```{r, echo=FALSE}
rescompprojects_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Applying for grants / funding:

```{r, echo=FALSE}
rescompfunding_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

__[7.2] Academic community activities__

```{r, echo=FALSE}
bind_rows(reseditor_schtype,resreviewer_schtype,resorganiser_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>%
  spread(Variable, prop) %>% 
  select( "Scheme Type"=SchemeType,"Journal Editor"=ResEditor,"Peer reviewer"=ResReviewer,"Conference organiser" = ResOrganiser) %>%
  pander

```

__[7.3] International collaboration__ 

Research activities with colleagues from outside Scholar's country of origin or based outisde the Scholar's country of origin.


Collaborative authorship of papers:

```{r, echo=FALSE}
rescollabauthor_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Collaborative applications for grants:

```{r, echo=FALSE}

rescollabgrant_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>%
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Attendance at international conferences:

```{r, echo=FALSE}

rescollabconf_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

# 8. Teaching

Overall involvement in teaching:

```{r, echo=FALSE}
teachmain_schtype %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-Response,-Variable, "Scheme Type"=SchemeType,Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

Levels of education at which Scholars are teaching (note - a single Scholar may teach at multiple levels: percentages are proportion of the category who reported teaching at that level):

```{r, echo=FALSE}
rbind(teachschool_schtype,teachundergrad_schtype,teachpostgrad_schtype,teachdoctorate_schtype,teachtvet_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable,prop) %>% 
  select(SchemeType,Doctoral=TeachDoctorate,Postgraduate=TeachPostgrad,Undergraduate=TeachUndergrad,TVET=TeachTVET,School=TeachSchool) %>% 
  pander

```

# 9. Networks and links

Frequency of contact with networks of various kinds.

Academic contacts at UK host institution:

```{r, echo=FALSE}
netacad_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>% 
  pander

```

Professional networks in the UK:

```{r, echo=FALSE}
netuk_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>% 
  pander
```

Professional networks in the Scholar's home country:

```{r, echo=FALSE}
nethome_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>% 
  pander
```

Professional networks elsewhere abroad:

```{r, echo=FALSE}
netother_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>% 
  pander
```

Personal networks abroad:

```{r, echo=FALSE}
netpersonal_schtype %>% 
  select(-freq, -Variable, "Scheme Type"= SchemeType) %>% 
  spread(Response,prop) %>% 
  pander
```

# 10. Broader impact

Proportion of Scholars who reported impact at different breadths:

```{r, echo=FALSE}
bind_rows(impinstitutional_schtype,implocal_schtype,impnational_schtype,impinternational_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>% 
  select("Scheme Type" = SchemeType, Institutional=ImpInstitutional,Local=ImpLocal,National=ImpNational,International=ImpInternational) %>%
  pander

```

Types of impact reported:

```{r, echo=FALSE}
bind_rows(impsocial_schtype,impcivic_schtype,impecon_schtype,imppolicy_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>%
  rename("Scheme Type" = SchemeType,"Civic Engagement"=ImpCivic, "Economic Development" = ImpEcon,
         "Policymaking"=ImpPolicy, "Social Development" =ImpSocial) %>% 
  pander

```

# 11. Analytic indices

Comparative indices, ranging from 0 (lowest) to 1 (highest), based on responses to questions on application of skills, leadership, research activity, and international research collaboration. Methodology detailed elsewhere: please contact the CSC E&M Team for details.

```{r, echo=FALSE}
bind_cols(select(indexskills_schtype, "Scheme Type" = SchemeType, Skills=Mean),
          select(indexldr_schtype, Leadership=Mean),
          select(indexresearch_schtype, "Research productivity"=Mean),
          select(indexcollab_schtype, "Research collaboration"=Mean)) %>% 
  pander

```





