---
title: '2016 Alumni surveys: Scheme Type Breakdown'
author: "CSC E&M Team"
date: "13 April 2017"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include = FALSE}

source("S:/SCHOLARSHIPS/CSC/SCHEMES/CSFP-IN/CSC-Evaluation/Data Management Crystal Snap IT/r_codebank/2016_sch_long/2016_sch_long_basicanalysis.r")

library(pacman)
pacman:: p_load(tidyverse, pander,knitr, RODBC)

set.alignment("left", permanent = T)
panderOptions("table.split.table",Inf)

```

This document relates to `r SurveyName` and is a intended as a short overview of basic findings by a key variable. For more detailed interpretation or explanation of the figures, please contact the evaluation team: [evaluation@cscuk.org.uk](mailto:evaluation@cscuk.org.uk)

# 1. Data overview

```{r, echo=FALSE}
overview_schtype %>% 
  select(-Variable,Count=freq, 'Proportion (%)'=prop) %>% 
  pander
```

# 2. Current residency

```{r, echo=FALSE}
bind_rows(rescountry_schtype,resregion_schtype) %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable, "Country"="resStatusCountry","Region"="resStatusRegion")) %>% 
  spread(SchemeType, prop) %>% 
  pander
```

# 3. Employment

Employment status:

```{r, echo=FALSE}
empcurrent_schtype %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Current Employment"="CurrentEmploy")) %>% 
  spread(SchemeType, prop) %>% 
  pander
```

Current sector of employment:

```{r, echo=FALSE}
empsector_schtype %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Current Job Sector"="CurrentSector")) %>% 
  spread(SchemeType, prop) %>% 
  pander
```

# 4. Further qualificiations

Study of additional qualifications post-Commonwealth Scholarship. Note: be cautious of low size for groups distorting figures.

```{r, echo=FALSE}
acapostaward_schtype %>% 
  filter(Response=="Yes") %>% 
  arrange(desc(prop)) %>% 
  select(-freq, -Response, "Proportion (%)"=prop) %>% 
  mutate(Variable = fct_recode(Variable,"Additional qualification"="AcaPostaward")) %>% 
  pander
```

Qualification levels (in rows: Scheme Type in columns):

```{r, echo=FALSE}
acaquallevel_schtype %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Qualification type"="AcaQualLevel")) %>% 
  spread(SchemeType, prop) %>% 
  pander
```

# 5. Leadership activities

Workplace related leadership activities:

```{r, echo=FALSE}
bind_rows(ldrbudget_schtype, ldrmanaging_schtype, ldrsupervise_schtype,ldrstrategy_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq, -Response) %>% 
  mutate(Variable = fct_recode(Variable,"Overseeing budgets"="LdrBudget","Managing Company / department" = "LdrManaging",
                               "Setting strategy"="LdrStrategy","Supervising others"="LdrSupervising")) %>% 
  spread(SchemeType, prop) %>% 
  pander
```

# 6. Skill application

Use of skills from Scholarship in various circumstances. Divided into three overall groups: 

[1] Use of skills

```{r, echo=FALSE}
bind_rows(
    appskillwork_schtype, appskillnonwork_schtype,appapproach_schtype) %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Used in workplace"="AppSkillWork", "Used elsewhere"="AppSkillNonwork",
                               "Took new approach"="AppApproachProblem")) %>% 
  spread(Response,prop) %>% 
  arrange(desc(Variable)) %>% 
  pander

```

[2] Knowledge transfer

```{r, echo=FALSE}
bind_rows(
    apptrain_schtype,appresources_schtype) %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Trained others"="AppTrainColleagues","Developed resources" = "AppDevelopResources")) %>% 
  spread(Response,prop) %>% 
  pander

```

[3] Advocacy and influencing change

```{r, echo=FALSE}
bind_rows(
    appadvocate_schtype,appchange_schtype) %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Advocated change"="AppAdvocateChange","Introduced change"="AppMakeChange")) %>% 
  spread(Response,prop) %>% 
  pander

```

# 7. Research activity

Overall involvement in academic research:

```{r, echo=FALSE}
resmain_schtype %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-freq, -Response, "Proportion (%)"=prop) %>% 
  mutate(Variable = fct_recode(Variable,"Research involvement"="ResMain")) %>% 
  pander
```

Academic productivity

```{r, echo=FALSE}

bind_rows(rescomparticles_schtype,rescompprojects_schtype,rescompfunding_schtype) %>% 
  filter(!Response=="NA") %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Published articles"="ResCompArticles","Applied for funding"="ResCompFunding",
                               "Involved in projects" = "ResCompProjects")) %>% 
  spread(Response,prop) %>% 
  pander

```

Academic community activities:

```{r, echo=FALSE}
bind_rows(reseditor_schtype,resreviewer_schtype,resorganiser_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response, "Proportion (%)"=prop) %>%
  mutate(Variable = fct_recode(Variable,"Journal editor"="ResEditor","Peer reviewer"="ResReviewer",
                               "Conference organiser" = "ResOrganiser")) %>%
  pander


```

International collaboration 9activities with colleagues from outside Scholar's country of origin):

```{r, echo=FALSE}

bind_rows(rescollabauthor_schtype,rescollabgrant_schtype,rescollabconf_schtype) %>% 
  filter(!Response=="NA") %>% 
  select(-freq) %>% 
  mutate(Variable = fct_recode(Variable,"Authored articles"="ResCollabAuthor","Applied for grants"="ResCollabGrant",
                               "Attended conference" = "ResCollabConf")) %>% 
  spread(Response,prop) %>% 
  pander

```

# 8. Teaching

Overall involvement in teaching:

```{r, echo=FALSE}
teachmain_schtype %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-freq, -Response, "Proportion (%)"=prop) %>% 
  mutate(Variable = fct_recode(Variable,"Teaching responsibility"="TeachMain")) %>% 
  pander
```

Levels of education at which Scholars are teaching:

```{r, echo=FALSE}
rbind(teachschool_schtype,teachundergrad_schtype,teachpostgrad_schtype,teachdoctorate_schtype,teachtvet_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable,prop) %>% 
  select(SchemeType,Doctoral=TeachDoctorate,Postgraduate=TeachPostgrad,Undergraduate=TeachUndergrad,TVET=TeachTVET,School=TeachSchool) %>% 
  pander
```

# 9. Networks and links

Frequency of contact with networks of various kinds:

```{r, echo=FALSE}
rbind(netacad_schtype,netuk_schtype,nethome_schtype,netother_schtype,netpersonal_schtype) %>% 
  select(-freq) %>% 
  spread(SchemeType, prop) %>% 
  mutate(Variable = fct_recode(Variable,"Academic"="NetAcad", "Professional (UK)"="NetUK", "Pofessional (Home)"="NetHome",
         "Personal"="NetPersonal", "Other"="NetOther")) %>% 
  pander

```

# 10. Broader impact

Breadth of impact reported:

```{r, echo=FALSE}
bind_rows(impinstitutional_schtype,implocal_schtype,impnational_schtype,impinternational_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>% 
  select(SchemeType, Institutional=ImpInstitutional,Local=ImpLocal,National=ImpNational,International=ImpInternational) %>%
  pander

```

Types of impact reported:

```{r, echo=FALSE}
bind_rows(impsocial_schtype,impcivic_schtype,impecon_schtype,imppolicy_schtype) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>%
  rename('Civic Engagement'=ImpCivic, Economic = ImpEcon,'Policymaking'=ImpPolicy, 'Social Development' =ImpSocial) %>% 
  pander


```

# 11. Analytic indices

```{r, echo=FALSE}
bind_cols(select(indexskills_schtype, SchemeType, Skills=Mean),
          select(indexldr_schtype, Leadership=Mean),
          select(indexresearch_schtype, "Research activity"=Mean),
          select(indexcollab_schtype, "Research collaboration"=Mean)) %>% 
  pander

```





