---
title: '2016 Alumni surveys: Selection Score Breakdown'
author: "CSC E&M Team"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  html_document: default
---


```{r, include = FALSE}

source("S:/SCHOLARSHIPS/CSC/SCHEMES/CSFP-IN/CSC-Evaluation/Data Management Crystal Snap IT/r_codebank/2016_sch_long/2016_sch_long_basicanalysis.r")

library(pacman)
pacman:: p_load(tidyverse, pander,knitr, RODBC)

set.alignment("left", permanent = T)
panderOptions("table.split.table",Inf)

```

This document relates to `r SurveyName` and is a intended as a short overview of basic findings by a key variable. Selection score is the committee-asigned score a candidate receives at application to become a Commonwealth Scholar. Each score is constituted by several grades which are weighted to create a final score. The weighting for scores and quality of the applications may differ subtly from year to year, and scoring is only relevant in comparison to other candidates for the same funding (e.g. A split-site candidate is never compared against a masters degree candidate during the scholarship selection process). Not all candidates receive selection scores: some scheme types (e.g. Shared Scholarships) do not use selection scores. As such, there are fewer cases for all topics than in other key variable comparisons (e.g. subject or gender).

To allow selection scoring data to be used for analysis, we create a standardised score based on the deviation of an individual candidate's score from the average score of candidates within the selection process in their year of application. Four groups are formed - Agency: Developed, Masters, PhD, Split site - and candidates for scholarships within those groups are assigned standardised scores within each application year. A positive standardised score indicates a higher than average selection score, while a negative standardised score indicates a selection score lower than average within the year of application.

For more detailed interpretation or explanation of the figures, please contact the evaluation team: [evaluation@cscuk.org.uk](mailto:evaluation@cscuk.org.uk)

# 1. Data overview

Counts of cases are not typically shown in the results tables; note should taken where the table below indicates few respondents in a particular category.

```{r, echo=FALSE}
overview_score %>% 
  select(-Variable,Group=Response,Cases=Freq) %>% 
  pander
```

# 2. Current residency

Residency in home country:

```{r, echo=FALSE}
rescountry_score %>% 
  mutate(Variable = fct_recode(Variable, "Country"="resStatusCountry")) %>% 
  select(-Variable, "Current residency"=Response,Cases=Freq) %>%
  pander
```

Residency in home region:

```{r, echo=FALSE}
resregion_score %>% 
  mutate(Variable = fct_recode(Variable, "Region"="resStatusRegion")) %>% 
  select(-Variable, "Current residency"=Response,Cases=Freq) %>%
  pander
```

# 3. Employment

Employment status:

```{r, echo=FALSE}
empcurrent_score %>% 
  mutate(Response = fct_recode(Response, "Other" = "Neither employed nor studying")) %>% 
  select(-Variable, "Employment status"=Response,Cases=Freq) %>% 
  pander
```

Current sector of employment of Scholars:

```{r, echo=FALSE}
empsector_score %>% 
  filter(!is.na(Response)) %>% 
  select(-Variable, "Employment sector"=Response,Cases=Freq) %>% 
  pander
```

# 4. Further qualificiations

Study of additional qualifications in the last two years. Note: be cautious of low size for groups distorting figures for these questions.

Respondents who had undertaken additional qualifications since completing their Commonwealth Scholarship:

```{r, echo=FALSE}
acapostaward_score %>% 
  arrange(desc(Response)) %>% 
  select(-Variable, "Further qualification" = Response, Cases=Freq) %>% 
  pander
```

Level of qualification studied:

```{r, echo=FALSE}
acaquallevel_score %>% 
  select(-Variable, "Qualification type"=Response,Cases=Freq) %>% 
  pander
```

# 5. Leadership activities

Workplace related leadership activities divided into four areas.

Overseeing budgets:

```{r, echo=FALSE}
ldrbudget_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>% 
  select(-Variable,Cases=Freq) %>%
  pander

```

Managing a company or department:

```{r, echo=FALSE}
ldrmanaging_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>% 
  select(-Variable,Cases=Freq) %>%
  pander

```

Setting strategy for an organisation:

```{r, echo=FALSE}
ldrstrategy_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>% 
  select(-Variable,Cases=Freq) %>%
  pander

```

Supervising others:

```{r, echo=FALSE}
ldrsupervise_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>% 
  select(-Variable,Cases=Freq) %>%
  pander

```

# 6. Skill application

Use of skills from Scholarship in various circumstances. Divided into three overall groups: Use of skills, knowledge transfer, and advocating for change.

__[6.1] Use of skills__

Three variables constitute the 'use of skills' group: application of skills learned during your studies in the workplace; application of skills learned during your studies outside of the workplace; and approaching a problem differently based on something learned during your studies.

Use of skills in the workplace:

```{r, echo=FALSE}
appskillwork_score %>% 
  select(-Variable,Cases=Freq) %>% 
  pander
```

Use of skills outside of the workplace:

```{r, echo=FALSE}
appskillnonwork_score %>% 
  select(-Variable,Cases=Freq) %>% 
  pander
```

Approach a problem differently:

```{r, echo=FALSE}
appapproach_score %>% 
  select(-Variable, Cases=Freq) %>% 
  pander
```

__[6.2] Knowledge transfer__

Two variables constitute the 'knowledge transfer' group: teaching a colleague something learned during your studies and developing training resources for others based something learned during your studies.

Teaching a colleague:

```{r, echo=FALSE}
apptrain_score %>% 
  select(-Variable,Cases=Freq) %>% 
  pander
```

Developing training resources:

```{r, echo=FALSE}
appresources_score %>% 
  select(-Variable, Cases=Freq) %>% 
  pander
```

__[6.3] Advocacy and influencing change__

Two variables constitute the 'advocacy and influencing change' group: Encouraging senior managers to make change based on something learned during your studies and making a change to your organisation's working practice based on something learned during your studies.

Encouraging senior managers to make change:

```{r, echo=FALSE}
appadvocate_score %>% 
  select(-Variable, Cases=Freq) %>% 
  pander
```

Personally making a change to organisational practice:

```{r, echo=FALSE}
appchange_score %>% 
  select(-Variable,Cases=Freq) %>% 
  pander
```

# 7. Research activity

Overall involvement in academic research:

```{r, echo=FALSE}
resmain_score %>% 
  filter(!is.na(Response)) %>%
  arrange(desc(Response)) %>% 
  select(-Variable, "Research activity"=Response, Cases=Freq) %>% 
  pander
```

__[7.1] Academic Productivity__

The category "Never" indicates a Scholar who has indicated involvement in academic research generally (i.e. answered 'yes' to the question in the table above), but has indicated that they are never involved in this specific academic activity (e.g. publishing journal articles). This applies to "7.1. Academic Productivity" and "7.3. Research Collaboration".

Publishing journal articles:

```{r, echo=FALSE}
rescomparticles_score %>% 
  filter(!is.na(Response)) %>% 
  select(-Variable, Cases=Freq) %>% 
  pander
```

Involvement in academic projects:

```{r, echo=FALSE}
rescompprojects_score %>% 
  filter(!is.na(Response)) %>% 
  select(-Variable, Cases=Freq) %>% 
  pander

```

Applying for grants / funding:

```{r, echo=FALSE}
rescompfunding_score %>% 
  filter(!is.na(Response)) %>% 
  select(-Variable, Cases=Freq) %>% 
  pander

```

__[7.2] Academic community activities__

Participation in the broader academic community, separated into three areas.

Acting as editor or steering group member for an academic journal:

```{r, echo=FALSE}
reseditor_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  select(-Variable, Cases=Freq) %>% 
  pander
```

Acting as a reviewer for an academic journal:

```{r, echo=FALSE}
reseditor_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  select(-Variable, Cases=Freq) %>%
  pander

```

Acting as an organiser for a research group or conference committee:

```{r, echo=FALSE}
resorganiser_score %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  select(-Variable, Cases=Freq) %>%
  pander

```

__[7.3] International collaboration__ 

Research activities with colleagues from outside Scholar's country of origin or based outisde the Scholar's country of origin.

Collaborative authorship of papers:

```{r, echo=FALSE}
rescollabauthor_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander

```

Collaborative applications for grants:

```{r, echo=FALSE}
rescollabgrant_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander

```

Attendance at international conferences:

```{r, echo=FALSE}
rescollabconf_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander

```

# 8. Teaching

Overall involvement in teaching:

```{r, echo=FALSE}
teachmain_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

__[8.1] Education levels of teaching__

Levels of education at which Scholars are teaching. Note: a single Scholar may teach at multiple levels.

School level:

```{r, echo=FALSE}
teachschool_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Undergraduate level:

```{r, echo=FALSE}
teachundergrad_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Postgraduate level:

```{r, echo=FALSE}
teachpostgrad_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Doctoral level:

```{r, echo=FALSE}
teachdoctorate_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Technical and Vocational Education (all levels):

```{r, echo=FALSE}
teachtvet_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

# 9. Networks and links

Frequency of contact with networks of various kinds.

Academic contacts at UK host institution:

```{r, echo=FALSE}
netacad_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander

```

Professional networks in the UK:

```{r, echo=FALSE}
netuk_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander
```

Professional networks in the Scholar's home country:

```{r, echo=FALSE}
nethome_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander
```

Professional networks elsewhere abroad:

```{r, echo=FALSE}
netother_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander
```

Personal networks abroad:

```{r, echo=FALSE}
netpersonal_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  pander
```

# 10. Broader impact

__[10.1] Impact breadth__

Proportion of Scholars who reported impact at different breadths.

Institutional level:

```{r, echo=FALSE}
impinstitutional_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Local level:

```{r, echo=FALSE}
implocal_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

National level:

```{r, echo=FALSE}
impnational_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

International level:

```{r, echo=FALSE}
impinternational_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

__[10.2] Impact type__

Proportion Scholars who reported impact in four categories.

Social development:

```{r, echo=FALSE}
impsocial_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Civic engagement:

```{r, echo=FALSE}
impcivic_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Economic development:

```{r, echo=FALSE}
impecon_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

Policymaking:

```{r, echo=FALSE}
imppolicy_score %>% 
  select(-Variable,Cases=Freq) %>% 
  filter(!is.na(Response)) %>% 
  arrange(desc(Response)) %>%
  pander
```

# 11. Analytic indices

Comparative indices, ranging from 0 (lowest) to 1 (highest), based on responses to questions on application of skills, leadership, research activity, and international research collaboration. Methodology detailed elsewhere: please contact the CSC E&M Team for details. Because both the standardised selection score ('Committee Z-score') and index score are continuous variables, they are visualised as scattergraphs. 

__Skill use index:__

```{r, echo=FALSE, warning=FALSE,fig.width=5, fig.height=4}
ggplot(alumni.data, aes(x=ZCtteeScore, y=i.skills)) + 
  geom_jitter() +
  coord_cartesian(ylim=c(0,1.0)) +
  ylab("Skills index") +
  xlab("Committee Z-score (SD)") +
  theme_bw()
```

__Leadership index:__

```{r, echo=FALSE, warning=FALSE,fig.width=5, fig.height=4}
ggplot(alumni.data, aes(x=ZCtteeScore, y=i.ldr)) + 
  geom_jitter() +
  coord_cartesian(ylim=c(0,1.0)) +
  ylab("Leadership index") +
  xlab("Committee Z-score (SD)") +
  theme_bw()
```

__Research productivity index:__

```{r, echo=FALSE, warning=FALSE,fig.width=5, fig.height=4}
ggplot(alumni.data, aes(x=ZCtteeScore, y=i.research)) + 
  geom_jitter() +
  coord_cartesian(ylim=c(0,1.0)) +
  ylab("Research productivity index") +
  xlab("Committee Z-score (SD)") +
  theme_bw()
```

__Research collaboration index:__

```{r, echo=FALSE,, warning=FALSE,fig.width=5, fig.height=4}
ggplot(alumni.data, aes(x=ZCtteeScore, y=i.collab)) + 
  geom_jitter() +
  coord_cartesian(ylim=c(0,1.0)) +
  ylab("Research collaboration index") +
  xlab("Committee Z-score (SD)") +
  theme_bw()
```

