---
title: '2016 Alumni surveys: Year Group Breakdown'
author: "CSC E&M Team"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}

source("S:/SCHOLARSHIPS/CSC/SCHEMES/CSFP-IN/CSC-Evaluation/Data Management Crystal Snap IT/r_codebank/2016_sch_long/2016_sch_long_basicanalysis.r")

library(pacman)
pacman:: p_load(tidyverse, pander,knitr, RODBC)

set.alignment("left", permanent = T)
panderOptions("table.split.table",Inf)

```

This document relates to `r SurveyName` and is a intended as a short overview of basic findings by a key variable. In the CSC longitudinal survey framework, alumni are assigned to 'year group' for the calendar year in which when they complete their Commonwealth Scholarship funding. Thus, a Scholar in the 2010 year group completed their funding in 2010. Each alumni survey includes five year groups: those 2, 4, 6, 8, and 10 years prior to the year of the survey. For instance, the 2016 survey would include the 2014, 2012, 2010, 2008, and 2006 year group Scholars.

Figures in tables are proportions (%) of the total (e.g. 89% of Split site Scholars replied 'Often') unless otherwise stated. For more detailed interpretation or explanation of the figures, please contact the evaluation team: [evaluation@cscuk.org.uk](mailto:evaluation@cscuk.org.uk)

# 1. Data overview

Counts of cases are not typically shown in the results tables; note should taken where the table below indicates few respondents in a particular category.

```{r, echo=FALSE}
overview_year %>% 
  arrange(desc(as.numeric(Response))) %>% 
  select(-Variable,"Year Group" = Response,Cases=freq, 'Proportion (%)'=prop) %>% 
  pander
```

# 2. Current residency

```{r, echo=FALSE}
bind_rows(rescountry_year,resregion_year) %>%
  filter(Response=="Home") %>% 
  select(-freq, -Response) %>% 
  mutate(Variable = fct_recode(Variable, "Country"="resStatusCountry","Region"="resStatusRegion")) %>% 
  spread(Variable, prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

# 3. Employment

Employment status:

```{r, echo=FALSE}
empcurrent_year %>% 
  select(-freq,-Variable) %>% 
  mutate(Response = fct_recode(Response, "Other" = "Neither employed nor studying")) %>% 
  spread(Response, prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  select("Year Group" = YearGroup, Employed, contains("Employed and studying"),Studying, Other) %>% 
  pander
```

Current sector of employment of Scholars (Note: percentages may not sum to 100%: proportions are of all Scholars in each category, including any not currently employed):

```{r, echo=FALSE}
empsector_year %>% 
  select(-freq,-Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response, prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

# 4. Further qualificiations

Study of additional qualifications in the last two years. Note: be cautious of low size for groups distorting figures for these questions.

Respondents who had undertaken additional qualifications since completing their Commonwealth Scholarship:

```{r, echo=FALSE}
acapostaward_year %>% 
  filter(Response=="Yes") %>%
  arrange(desc(YearGroup)) %>% 
  select(-Response,-Variable,"Year Group"=YearGroup, "Proportion (%)"=prop,"Cases"=freq) %>% 
  pander
```

Level of qualification studied (each level is shown as a proportion of respondents who had undertaken additional qualifications):

```{r, echo=FALSE}
acaquallevel_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  select("Year Group"=YearGroup, Doctorate,contains("Master's degree"),contains("Professional accreditation"),contains("Technical training"),
         contains("Undergraduate degree"), Other) %>% 
  pander
```

# 5. Leadership activities

Workplace related leadership activities:

```{r, echo=FALSE}
bind_rows(ldrbudget_year, ldrmanaging_year, ldrsupervise_year,ldrstrategy_year) %>% 
  filter(Response=="Yes") %>% 
  select(-freq, -Response) %>% 
  mutate(Variable = fct_recode(Variable,"Overseeing budgets"="LdrBudget","Managing Company / department" = "LdrManaging",
                               "Setting strategy"="LdrStrategy","Supervising others"="LdrSupervising")) %>% 
  spread(Variable, prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

# 6. Skill application

Use of skills from Scholarship in various circumstances. Divided into three overall groups: Use of skills, knowledge transfer, and advocating for change.

__[6.1] Use of skills__

Three variables constitute the 'use of skills' group: application of skills learned during your studies in the workplace; application of skills learned during your studies outside of the workplace; and approaching a problem differently based on something learned during your studies.

Use of skills in the workplace:

```{r, echo=FALSE}
appskillwork_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Use of skills outside of the workplace:

```{r, echo=FALSE}
appskillnonwork_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Approach a problem differently:

```{r, echo=FALSE}
appapproach_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

__[6.2] Knowledge transfer__

Two variables constitute the 'knowledge transfer' group: teaching a colleague something learned during your studies and developing training resources for others based something learned during your studies.

Teaching a colleague:

```{r, echo=FALSE}
apptrain_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Developing training resources:

```{r, echo=FALSE}
appresources_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

__[6.3] Advocacy and influencing change__

Two variables constitute the 'advocacy and influencing change' group: Encouraging senior managers to make change based on something learned during your studies and making a change to your organisation's working practice based on something learned during your studies.

Encouraging senior managers to make change:

```{r, echo=FALSE}
appadvocate_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Personally making a change to organisational practice:

```{r, echo=FALSE}
appchange_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

# 7. Research activity

Overall involvement in academic research:

```{r, echo=FALSE}
resmain_year %>% 
  filter(Response=="Yes") %>%
  arrange(desc(YearGroup)) %>% 
  select(-Response,-Variable,"Year Group" = YearGroup,Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

__[7.1] Academic Productivity__

Results do not sum to 100% in each row because some Scholars are not involved in academic research activity at all: these respondents are excluded from the table, but the proportions shown are based on all Scholars within each category, not _only_ Scholars involved in academic research. The category "Never" thus means a Scholar who has indicated involvement in academic research generally, but has indicated that they are never involved in this specific academic activity (e.g. publishing journal articles). This applies to "7.1. Academic Productivity" and "7.3. Research Collaboration".

Publishing journal articles:

```{r, echo=FALSE}
rescomparticles_year %>% 
  select(-freq, -Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Involvement in academic projects:

```{r, echo=FALSE}
rescompprojects_year %>% 
  select(-freq, -Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

Applying for grants / funding:

```{r, echo=FALSE}
rescompfunding_year %>% 
  select(-freq, -Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

__[7.2] Academic community activities__

```{r, echo=FALSE}
bind_rows(reseditor_year,resreviewer_year,resorganiser_year) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>%
  spread(Variable, prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  select("Year Group"=YearGroup,"Journal Editor"=ResEditor,"Peer reviewer"=ResReviewer,"Conference organiser" = ResOrganiser) %>%
  pander

```

__[7.3] International collaboration__ 

Research activities with colleagues from outside Scholar's country of origin or based outisde the Scholar's country of origin.


Collaborative authorship of papers:

```{r, echo=FALSE}
rescollabauthor_year %>% 
  select(-freq, -Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

Collaborative applications for grants:

```{r, echo=FALSE}

rescollabgrant_year %>% 
  select(-freq, -Variable) %>%
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

Attendance at international conferences:

```{r, echo=FALSE}

rescollabconf_year %>% 
  select(-freq, -Variable) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

# 8. Teaching

Overall involvement in teaching:

```{r, echo=FALSE}
teachmain_year %>% 
  filter(Response=="Yes") %>%
  arrange(desc(YearGroup)) %>% 
  select(-Response,-Variable,"Year Group"=YearGroup, Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

Levels of education at which Scholars are teaching (note - a single Scholar may teach at multiple levels: percentages are proportion of the category who reported teaching at that level):

```{r, echo=FALSE}
rbind(teachschool_year,teachundergrad_year,teachpostgrad_year,teachdoctorate_year,teachtvet_year) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  select("Year Group"=YearGroup,Doctoral=TeachDoctorate,Postgraduate=TeachPostgrad,
         Undergraduate=TeachUndergrad,TVET=TeachTVET,School=TeachSchool) %>% 
  pander

```

# 9. Networks and links

Frequency of contact with networks of various kinds.

Academic contacts at UK host institution:

```{r, echo=FALSE}
netacad_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander

```

Professional networks in the UK:

```{r, echo=FALSE}
netuk_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Professional networks in the Scholar's home country:

```{r, echo=FALSE}
nethome_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Professional networks elsewhere abroad:

```{r, echo=FALSE}
netother_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

Personal networks abroad:

```{r, echo=FALSE}
netpersonal_year %>% 
  select(-freq, -Variable) %>% 
  spread(Response,prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup) %>% 
  pander
```

# 10. Broader impact

Proportion of Scholars who reported impact at different breadths:

```{r, echo=FALSE}
bind_rows(impinstitutional_year,implocal_year,impnational_year,impinternational_year) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>% 
  arrange(order(YearGroup,decreasing=T)) %>% 
  select("Year Group"=YearGroup, Institutional=ImpInstitutional,Local=ImpLocal,National=ImpNational,International=ImpInternational) %>%
  pander

```

Types of impact reported:

```{r, echo=FALSE}
bind_rows(impsocial_year,impcivic_year,impecon_year,imppolicy_year) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>%
  arrange(order(YearGroup,decreasing=T)) %>% 
  rename("Year Group"=YearGroup,"Civic Engagement"=ImpCivic, "Economic Development" = ImpEcon,
         "Policymaking"=ImpPolicy, "Social Development" =ImpSocial) %>% 
  pander

```

# 11. Analytic indices

Comparative indices, ranging from 0 (lowest) to 1 (highest), based on responses to questions on application of skills, leadership, research activity, and international research collaboration. Methodology detailed elsewhere: please contact the CSC E&M Team for details.

```{r, echo=FALSE}
bind_cols(select(indexskills_year,"Year Group"=YearGroup, Skills=Mean),
          select(indexldr_year, Leadership=Mean),
          select(indexresearch_year, "Research productivity"=Mean),
          select(indexcollab_year, "Research collaboration"=Mean)) %>% 
  pander

```





