---
title: '2016 Alumni surveys: Degree Subject Breakdown'
author: "CSC E&M Team"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  html_document: default
---


```{r, include = FALSE}

source("S:/SCHOLARSHIPS/CSC/SCHEMES/CSFP-IN/CSC-Evaluation/Data Management Crystal Snap IT/r_codebank/2016_sch_long/2016_sch_long_basicanalysis.r")

library(pacman)
pacman:: p_load(tidyverse, pander,knitr, RODBC)

set.alignment("left", permanent = T)
panderOptions("table.split.table",Inf)

```

This document relates to `r SurveyName` and is a intended as a short overview of basic findings by a key variable. Figures in tables are proportions (%) of the total (e.g. 89% of Split site Scholars replied 'Often') unless otherwise stated. Subjects of study are standardised by the JACS 3.0 categories, produced by the Higher Education Statistics Agency (UK). In this document only JACS Categories (top level subject coding) are used. For more detailed interpretation or explanation of the figures, please contact the evaluation team: [evaluation@cscuk.org.uk](mailto:evaluation@cscuk.org.uk)

# 1. Data overview

Counts of cases are not typically shown in the results tables; note should taken where the table below indicates few respondents in a particular category. In this document, only categories with at least 20 cases are included in results tables (other than the overview table below).

```{r, echo=FALSE}
overview_jacs %>% 
  select(-Variable,Subject=Response,Cases=freq, 'Proportion (%)'=prop) %>% 
  pander
```

# 2. Current residency

```{r, echo=FALSE}
bind_rows(rescountry_jacs,resregion_jacs) %>% 
  filter(Response=="Home") %>% 
  select(-freq, -Response, Subject=JacsCat) %>% 
  mutate(Variable = fct_recode(Variable, "Country"="resStatusCountry","Region"="resStatusRegion")) %>% 
  spread(Variable, prop) %>% 
  arrange(desc(Country)) %>% 
  pander
```

# 3. Employment

Employment status:

```{r, echo=FALSE}
empcurrent_jacs %>% 
  select(-freq,-Variable, Subject=JacsCat) %>% 
  mutate(Response = fct_recode(Response, "Other" = "Neither employed nor studying")) %>% 
  spread(Response, prop) %>% 
  select(Subject, Employed, contains("Employed and studying"),Studying, Other) %>% 
  arrange(desc(Employed)) %>% 
  pander
```

Current sector of employment of Scholars (Note: percentages may not sum to 100%: proportions are of all Scholars in each category, including any not currently employed):

```{r, echo=FALSE}
empsector_jacs %>% 
  select(-freq,-Variable,Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response, prop) %>% 
  pander
```

# 4. Further qualificiations

Study of additional qualifications in the last two years. Note: be cautious of low size for groups distorting figures for these questions.

Respondents who had undertaken additional qualifications since completing their Commonwealth Scholarship:

```{r, echo=FALSE}
acapostaward_jacs %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select( -Response,-Variable, "Proportion (%)"=prop,"Cases"=freq, Subject=JacsCat) %>% 
  pander
```

Level of qualification studied (each level is shown as a proportion of respondents who had undertaken additional qualifications). Note: entries are not limited to subjects with 20 or more cases so be cautious of how results might be distorted by low numbers of cases.

```{r, echo=FALSE}
acaquallevel_jacs %>% 
  select(-freq, -Variable,Subject=JacsCat, "Degree studied"=Response) %>% 
  spread("Degree studied",prop) %>% 
  select(Subject, Doctorate,contains("Master's degree"),contains("Professional accreditation"),contains("Technical training"),
         contains("Undergraduate degree"), Other) %>% 
  pander
```

# 5. Leadership activities

Workplace related leadership activities:

```{r, echo=FALSE}
bind_rows(ldrbudget_jacs, ldrmanaging_jacs, ldrsupervise_jacs,ldrstrategy_jacs) %>% 
  filter(Response=="Yes") %>% 
  select(-freq, -Response,Subject=JacsCat) %>% 
  mutate(Variable = fct_recode(Variable,"Overseeing budgets"="LdrBudget","Managing Company / department" = "LdrManaging",
                               "Setting strategy"="LdrStrategy","Supervising others"="LdrSupervising")) %>% 
  spread(Variable, prop) %>% 
  pander
```

# 6. Skill application

Use of skills from Scholarship in various circumstances. Divided into three overall groups: Use of skills, knowledge transfer, and advocating for change.

__[6.1] Use of skills__

Three variables constitute the 'use of skills' group: application of skills learned during your studies in the workplace; application of skills learned during your studies outside of the workplace; and approaching a problem differently based on something learned during your studies.

Use of skills in the workplace:

```{r, echo=FALSE}
appskillwork_jacs %>% 
  select(-freq, -Variable,Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

Use of skills outside of the workplace:

```{r, echo=FALSE}
appskillnonwork_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

Approach a problem differently:

```{r, echo=FALSE}
appapproach_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

__[6.2] Knowledge transfer__

Two variables constitute the 'knowledge transfer' group: teaching a colleague something learned during your studies and developing training resources for others based something learned during your studies.

Teaching a colleague:

```{r, echo=FALSE}
apptrain_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

Developing training resources:

```{r, echo=FALSE}
appresources_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

__[6.3] Advocacy and influencing change__

Two variables constitute the 'advocacy and influencing change' group: Encouraging senior managers to make change based on something learned during your studies and making a change to your organisation's working practice based on something learned during your studies.

Encouraging senior managers to make change:

```{r, echo=FALSE}
appadvocate_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

Personally making a change to organisational practice:

```{r, echo=FALSE}
appchange_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  spread(Response,prop) %>%
  pander
```

# 7. Research activity

Overall involvement in academic research:

```{r, echo=FALSE}
resmain_jacs %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-Response,-Variable,  Subject=JacsCat,Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

__[7.1] Academic Productivity__

Results do not sum to 100% in each row because some Scholars are not involved in academic research activity at all: these respondents are excluded from the table, but the proportions shown are based on all Scholars within each category, not _only_ Scholars involved in academic research. The category "Never" thus means a Scholar who has indicated involvement in academic research generally, but has indicated that they are never involved in this specific academic activity (e.g. publishing journal articles). This applies to "7.1. Academic Productivity" and "7.3. Research Collaboration".

Publishing journal articles:

```{r, echo=FALSE}
rescomparticles_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>%
  pander
```

Involvement in academic projects:

```{r, echo=FALSE}
rescompprojects_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Applying for grants / funding:

```{r, echo=FALSE}
rescompfunding_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

__[7.2] Academic community activities__

```{r, echo=FALSE}
bind_rows(reseditor_jacs,resreviewer_jacs,resorganiser_jacs) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>%
  spread(Variable, prop) %>% 
  select(Subject=JacsCat,"Journal Editor"=ResEditor,"Peer reviewer"=ResReviewer,"Conference organiser" = ResOrganiser) %>%
  pander

```

__[7.3] International collaboration__ 

Research activities with colleagues from outside Scholar's country of origin or based outisde the Scholar's country of origin.


Collaborative authorship of papers:

```{r, echo=FALSE}
rescollabauthor_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Collaborative applications for grants:

```{r, echo=FALSE}

rescollabgrant_jacs %>% 
  select(-freq, -Variable,  Subject=JacsCat) %>%
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

Attendance at international conferences:

```{r, echo=FALSE}

rescollabconf_jacs %>% 
  select(-freq, -Variable,Subject=JacsCat) %>% 
  filter(!is.na(Response)) %>% 
  spread(Response,prop) %>% 
  pander

```

# 8. Teaching

Overall involvement in teaching:

```{r, echo=FALSE}
teachmain_jacs %>% 
  filter(Response=="Yes") %>%
  arrange(desc(prop)) %>% 
  select(-Response,-Variable, Subject=JacsCat,Cases=freq, "Proportion (%)"=prop) %>% 
  pander
```

Levels of education at which Scholars are teaching (note - a single Scholar may teach at multiple levels: percentages are proportion of the category who reported teaching at that level):

```{r, echo=FALSE}
rbind(teachschool_jacs,teachundergrad_jacs,teachpostgrad_jacs,teachdoctorate_jacs,teachtvet_jacs) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable,prop) %>% 
  select(Subject=JacsCat,Doctoral=TeachDoctorate,Postgraduate=TeachPostgrad,
         Undergraduate=TeachUndergrad,TVET=TeachTVET,School=TeachSchool) %>% 
  pander

```

# 9. Networks and links

Frequency of contact with networks of various kinds.

Academic contacts at UK host institution:

```{r, echo=FALSE}
netacad_jacs %>% 
  select(-freq, -Variable, Subject=JacsCat) %>% 
  spread(Response,prop) %>% 
  pander

```

Professional networks in the UK:

```{r, echo=FALSE}
netuk_jacs %>% 
  select(-freq, -Variable,Subject=JacsCat) %>% 
  spread(Response,prop) %>% 
  pander
```

Professional networks in the Scholar's home country:

```{r, echo=FALSE}
nethome_jacs %>% 
  select(-freq, -Variable, Subject=JacsCat) %>% 
  spread(Response,prop) %>% 
  pander
```

Professional networks elsewhere abroad:

```{r, echo=FALSE}
netother_jacs %>% 
  select(-freq, -Variable, Subject=JacsCat) %>% 
  spread(Response,prop) %>% 
  pander
```

Personal networks abroad:

```{r, echo=FALSE}
netpersonal_jacs %>% 
  select(-freq, -Variable, Subject=JacsCat) %>% 
  spread(Response,prop) %>% 
  pander
```

# 10. Broader impact

Proportion of Scholars who reported impact at different breadths:

```{r, echo=FALSE}
bind_rows(impinstitutional_jacs,implocal_jacs,impnational_jacs,impinternational_jacs) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>% 
  select( Subject=JacsCat, Institutional=ImpInstitutional,Local=ImpLocal,National=ImpNational,International=ImpInternational) %>%
  pander

```

Types of impact reported:

```{r, echo=FALSE}
bind_rows(impsocial_jacs,impcivic_jacs,impecon_jacs,imppolicy_jacs) %>% 
  filter(Response=="Yes") %>% 
  select(-freq,-Response) %>% 
  spread(Variable, prop) %>%
  rename(Subject=JacsCat,"Civic Engagement"=ImpCivic, "Economic Development" = ImpEcon,
         "Policymaking"=ImpPolicy, "Social Development" =ImpSocial) %>% 
  pander

```

# 11. Analytic indices

Comparative indices, ranging from 0 (lowest) to 1 (highest), based on responses to questions on application of skills, leadership, research activity, and international research collaboration. Methodology detailed elsewhere: please contact the CSC E&M Team for details.

```{r, echo=FALSE}
bind_cols(select(indexskills_jacs, Subject=JacsCat, Skills=Mean),
          select(indexldr_jacs, Leadership=Mean),
          select(indexresearch_jacs, "Research productivity"=Mean),
          select(indexcollab_jacs, "Research collaboration"=Mean)) %>% 
  pander

```
